Introductory Physics Labs: A Tale of Two Transformations

### 2021-05-05 manuscript/onlineLabPaper.tex
I unmasked the manuscript and created the word doc.  Still need to tweak a few things.

% \author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
% 5\textsuperscript{th} street, Greenville, NC 27858 USA} \author{Mark W.\ Sprague}
% \affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
% street, Greenville, NC 27858 USA}

\author{First Author} \affiliation{Masked Institution}

\author{Second Author} \affiliation{Masked Institution}

@@

Labs are supervised by Author 2, but sections are run by Graduate TAs (GTAs). The transformed
curriculum was jointly written by both of the authors.  GTA training was also greatly enhanced
when the new lab curriculum was put in place.  Both authors, along with colleagues in Biology
and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics as these
disciplines are all using the same curricular format for their labs.  Author 2 runs a weekly
prep meeting with the GTAs, and Author 1 and the research team have supervised various aspects
of the transformation especially important for research such as curricular implementation
\citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019mask}.

\section{Transformation \#1: Argument Driven Inquiry}
Argument Driven Inquiry (ADI) is a pedagogical method developed to make science labs in school
better match what transpires in authentic research settings
\citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
answer questions, or measure quantities, that are well-known using procedures that have been
refined over time.  In ADI labs, we give students a guiding question to answer experimentally
(e.g., ``Does the force a fan exerts on a cart depend on the mass of the cart?''). This allows
students to design a procedure for an experiment that will answer that question, collect and
analyze their data, and make claims based on their data.  We accomplish this by having students
engage in a three-part cycle:
\begin{itemize}
  \item Pre-Lab - Introducing the context
  \item Proposal Development and Data Collection
  \item Argumentation and Peer Review
\end{itemize}
In the sections below, we will comment on each part of the cycle, focusing on both students and
GTAs. Each lab course completes at least three cycles (usually four in the Fall and Spring),
and the semester ends with a practical exam where students engage in this process on a
shortened cycle without peer feedback.\cite{Wolf2019mask} We have provided supplemental
materials with more details about each of the labs in our curriculum.

@@

Many students could not or did not attend the online WebEx sessions or participate with their
assigned groups.  Once they left campus, many students found they had increased work or school
responsibilities (\SI{42.1}{\percent}) or additional family responsibilities
(\SI{59.0}{\percent}).\citep{ECUcovidSurveyRedacted} We removed non-participating students from
groups and gave them an opportunity to make up their missed work asynchronously. Less than
\SI{50}{\percent} of the students in the make-up groups completed their work.

@@

\begin{acknowledgments}
  Redacted for review.% This work has been supported by the NSF (Award \# 1725655). We would
  % also like to thank the Physics GTAs who have helped us develop
  % resources and tutorials for students during this transition.
\end{acknowledgments}

>>>>

\author{Steven F.\ Wolf} \affiliation{East Carolina University Department of Physics 1000 E.\
  5\textsuperscript{th} street, Greenville, NC 27858 USA}

\author{Mark W.\ Sprague}
\affiliation{East Carolina University Department of Physics 1000 E.\ 5\textsuperscript{th}
street, Greenville, NC 27858 USA}

@@

Labs are supervised by MWS, but sections are run by Graduate TAs (GTAs). The transformed
curriculum was jointly written by both of the authors.  GTA training was also greatly enhanced
when the new lab curriculum was put in place.  Both authors, along with colleagues in Biology
and Chemistry, run training for all GTAs in Biology, Chemistry, Geology, and Physics as these
disciplines are all using the same curricular format for their labs.  MWS runs a weekly prep
meeting with the GTAs, and SFW and the research team have supervised various aspects of the
transformation especially important for research such as curricular implementation
\citep{SmithJoyner2020} and assessment grading practices \citep{Wolf2019}.

\section{Transformation \#1: Argument Driven Inquiry}
Argument Driven Inquiry (ADI) is a pedagogical method developed to make science labs in school
better match what transpires in authentic research settings
\citep{Walker2011,Sampson2011,Walker2016}.  In traditional labs, we often ask students to
answer questions, or measure quantities, that are well-known using procedures that have been
refined over time.  In ADI labs, we give students a guiding question to answer experimentally
(e.g., ``Does the force a fan exerts on a cart depend on the mass of the cart?''). This allows
students to design a procedure for an experiment that will answer that question, collect and
analyze their data, and make claims based on their data.  We accomplish this by having students
engage in a three-part cycle:
\begin{itemize}
  \item Pre-Lab - Introducing the context
  \item Proposal Development and Data Collection
  \item Argumentation and Peer Review
\end{itemize}
In the sections below, we will comment on each part of the cycle, focusing on both students and
GTAs. Each lab course completes at least three cycles (usually four in the Fall and Spring),
and the semester ends with a practical exam where students engage in this process on a
shortened cycle without peer feedback.\cite{Wolf2019} We have provided supplemental
materials with more details about each of the labs in our curriculum.

@@

Many students could not or did not attend the online WebEx sessions or participate with their
assigned groups.  Once they left campus, many students found they had increased work or school
responsibilities (\SI{42.1}{\percent}) or additional family responsibilities
(\SI{59.0}{\percent}).\citep{ECUcovidSurvey} We removed non-participating students from
groups and gave them an opportunity to make up their missed work asynchronously. Less than
\SI{50}{\percent} of the students in the make-up groups completed their work.

@@

\begin{acknowledgments}
  This work has been supported by the NSF (Award \# 1725655). We would
  also like to thank the Physics GTAs who have helped us develop
  resources and tutorials for students during this transition.
\end{acknowledgments}
